Unshuffling Permutations

### 2015-09-27 submission.tex
Typos

  As for \emph{2}, suppose, still aiming at a contradiction, that there
  exist two $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in
  $\mathcal{M}$. Since $\mathcal{M}$ is containment-free, we may assume
  $a < b$ and $a' < b'$. Therefore, we have $\pi(a) > \pi(b)$ (since
  $\sigma_1$ is decreasing) and $\pi(a') < \pi(b')$ (since $\sigma_2$ is
  increasing), which contradicts our hypothesis about~$\mathcal{M}$.
  \qed
\end{proof}

\bigskip

\begin{proof}[of Proposition~\ref{proposition:hardness}]
  Suppose first that $\sigma$ occurs in $\pi$ and fix an occurrence.
  Construct a matching $\mathcal{M}$ as follows:
  \begin{itemize}
    \item $\mathcal{M}$ contains $N_1$ pairwise crossing
    $(\nu_1, \nu'_1)$-edges.
    \item $\mathcal{M}$ contains $N_2$ pairwise crossing
    $(\nu_2, \nu'_2)$-edges.
    \item $\mathcal{M}$ contains $N_3$ pairwise crossing
    $(\nu_3, \nu'_3)$-edges.
    \item $\mathcal{M}$ contains $N_4$ pairwise crossing
    $(\nu_4, \nu'_4)$-edges.
    \item $\mathcal{M}$ contains $k+2$ pairwise crossing
    $(\sigma', \pi')$-edges as depicted in
    Figure~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely,
    (i) the first position of $\sigma'$
    (\emph{i.e.}, $(2N_1+N_2+N_3) + 1$) is linked
    to the first position of $\pi'$
    (\emph{i.e.}, $(2N_1 + 2N_2 + 2N_3 + N_4 + k + 2) + 1$),
    (ii) the last position of $\sigma'$
    (\emph{i.e.}, $(2N_1+N_2+N_3) + k+2$) is linked
    to the last position of $\pi'$
    (\emph{i.e.}, $(2N_1 + 2N_2 + 2N_3 + N_4 + k + 2) + n+2$),
    and all other positions in $\sigma'$ are linked by means of $k$ pairwise
    crossing edges to the positions in
    $\pi'$ that correspond to the fixed occurence of $\sigma$ in $\pi$.
    (Notice that we use here the fact that $\sigma$ occurs in $\pi$).
    \item $\mathcal{M}$ contains $n-k$ pairwise crossing
    $(\pi', \pi'')$-edges as depicted in
    Figure~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely,
    all positions in $\pi'$ that do not correspond to the fixed occurence of
    $\sigma$ in $\pi$ are linked by means of $n-k$ pairwise crossing edges
    to the positions in $\pi''$ that do not correspond to the fixed
    occurrence of $\sigma$ in $\pi$.
    \item $\mathcal{M}$ contains $k$ pairwise crossing
    $(\pi'', \sigma'')$-edges as depicted in
    Figure~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely, the positions in $\pi''$ that correspond to
    the fixed occurrence of $\sigma$ in $\pi$ are llinked
    linked by means of $k$ pairwise crossing edges to all positions in
    $\sigma''$.
    (Notice that we use here the fact that $\sigma$ occurs in $\pi$).
  \end{itemize}
  It can be easily checked (probably referring to Figure~\ref{fig:reduction}) that
  $\mathcal{M}$ is perfect, containment-free and that
  for any two disctinct edges
  $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.

@@

        input permutation $\sigma = 312$ and $\pi = 4\mathbf{5}\mathbf{2}1\mathbf{3}6$

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_1, \nu_2)$-edge $e = (a, a')$ in $\mathcal{M}$.
    Under this assumption, we show that $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Indeed, suppose, aiming at a contradiction,
    that there exists a $(\nu_1, \nu_1)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free,
    we must have $x < a$.
    Then it follows that $\mu(x) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(x') > \mu(a')$ (since $\nu_1$ is above $\nu_2$),
    which contradicts our hypothesis about $\mathcal{M}$.
    Hence $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Furthermore, since $\nu_1$ is increasing and
    there exists only one $(\nu_1, \nu_2)$-edge $(a, a')$ in $\mathcal{M}$,
    we conclude that
    $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges.
    But $|\nu_1| = |\nu'_1| = N_1$ and $\mathcal{M}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-edge,
      say $(y', y)$. Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item Position $y$ is not involved in a $(\nu_2, \nu'_1)$-edge.
      Since $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges
      in $\mathcal{M}$ and $|\nu'_1| = N_1$, there exists an edge $(y, y'')$ in $\mathcal{M}$
      that is neither a $(\nu_1, \nu'_1)$-edge nor a $(\nu_2, \nu'_1)$-edge
      nor a $(\nu'_1, \nu'_1)$-edge.
      In other words, $y'' > 2N_1 + N_2$.
      Now, for any $(\nu_1, \nu'_1)$-edge $(x, x')$ in $\mathcal{M}$, we
      have $\mu(x) < \mu(y)$ (since $\nu_1$ is below $\nu'_1$)
      and $\mu(x') > \mu(y'')$ (since $\nu'_1$ is above any other gadget),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:(nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then it follows that there exists an edge $(x, x')$ in $\mathcal{M}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-edge (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$ (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ is containment-free,
    there is neither a $(\nu_2, \nu_2)$-edge nor a $(\nu'_1, \nu'_1)$-edge
    in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an edge $(y, y'$ of $\mathcal{M}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would not be containment-free).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an edge in $\mathcal{M}$.
    Then it follows that $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:(nu_1, nu'_1)-edge} with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor a $(\nu_1, \nu'_1)$-edge
    nor a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:(nu_2, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is no
    $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
    Notice that there is neither
    a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_2, \nu_2)$-edge (Claim~\ref{claim:no (nu_2, nu_2)-edge})
    nor a $(\nu_2, \nu'_1)$-edge (Claim~\ref{claim:no (nu_2, nu'_1)-edge})
    in $\mathcal{M}$.
    But $|\nu_2| = N_2 > 2N_3 + 2N_4 + 2n + 2k +4$.
    Hence $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no edge below (nu_2, nu'_2)-edge}]
    Combine Claim~\ref{claim:(nu_2, nu'_2)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim: no edge right of nu'_2}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ contains an edge $(a, a')$ which is
    either a $(\nu'_2, \nu'_3)$-edge
    or a $(\nu'_2, \pi')$-edge
    or a $(\nu'_2, \nu'_4)$-edge
    or a $(\nu'_2, \pi'')$-edge
    or a $(\nu'_2, \sigma'')$-edge.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge},
    there exists a $(\nu_2, \nu'_2)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) > \mu(a)$ (since $\nu_2$ is above $\nu'_2$) and
    $\mu(b') < \mu(a')$ (since $\nu'_3$, $\pi'$, $\nu'_4$, $\pi''$ and
    $\sigma''$ are all above $\nu'_2$),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_3, nu'_2)-edge}]
    Suppose, aiming at a contradiction, that there exists
    $(\nu_3, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge}, there
    exists at least one $(\nu_2, \nu'_2)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free (Lemma~\ref{lemma:matching}),
    we have $x' < a'$.
    Therefore,
    we have $\mu(x) < \mu(a)$ (since $\nu_2$ is below $\nu_3$) and
    $\mu(x') > \mu(a')$ (since $\nu'_2$ is decreasing),
    which contradicts our hypothesis about $\mathcal{M}$.
    See Fig.~\ref{fig:subfig:no (nu_3, nu'_2)-edge}.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:at most one (nu_2, nu_3)-edge}]
    Apply Lemma~\ref{lemma:at most one edge monotone}.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_3)-edge and no (nu'_1, nu_3)-edge}]
    We first prove that there is no $(\nu_1, \nu_3)$-edge in $\mathcal{M}$.
    Indeed, suppose, aiming at a contradiction, that these exists
    a $(\nu_1, \nu_3)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have
    $b < a'$.
    Then it follows that
    $\mu(b) < \mu(a)$ (since $\nu_1$ is incresing) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu_3$),
    which contradicts our hypothesis about $\mathcal{M}$.

    As for no $(\nu_1, \nu_3)$-edges in $\mathcal{M}$, suppose,
    aiming at a contradiction, that these exists
    a $(\nu'_1, \nu_3)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that
    $\mu(b) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu_3$),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:(nu_3, nu'_3)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_3, \nu'_3)$-edge in $\mathcal{M}$.
    Combining
    Claim~\ref{claim:no edge below (nu_2, nu'_2)-edge},
    Claim~\ref{claim:no (nu_3, nu'_2)-edge},
    Claim~\ref{claim:at most one (nu_2, nu_3)-edge}
    and Claim~\ref{claim:no (nu_1, nu_3)-edge and no (nu'_1, nu_3)-edge},
    we conclude that $N_3-1$ positions in $\nu_3$ are involved
    in edges of $\mathcal{M}$ that are
    neither ($\nu_1, \nu_3)$-edges,
    nor $(\nu_2, \nu_3)$-edges
    nor $(\nu'_1, \nu_3)$-edges
    nor $(\nu_3, \nu_3)$-edges.
    But $N_3 - 1 > 2N_4 + 2n + 2k + 4$ (the positions left) and hence
    $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_3, nu'_3)-edge}]
    Combine Claim~\ref{claim:(nu_3, nu'_3)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_4)-edge}]
    According to Claim~\ref{claim:all (nu_2, nu'_2)-edges},
    all positions in $\nu_2$ and $\nu'_2$ are involved in
    $(\nu_2, \nu'_2)$-edges in $\mathcal{M}$.
    \qed
  \end{proof}

>>>>

  As for \emph{2}, suppose, still aiming at a contradiction, that there
  exist two $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in
  $\mathcal{M}$. Since $\mathcal{M}$ is containment-free, we may assume
  $a < b$ and $a' < b'$. Therefore, we have $\pi(a) > \pi(b)$ (since
  $\sigma_1$ is decreasing) and $\pi(a') < \pi(b')$ (since $\sigma_2$ is
  increasing), which contradicts our hypothesis about~$\mathcal{M}$.
  \qed
\end{proof}
\bigskip

\begin{proof}[of Proposition~\ref{proposition:hardness}]
  Suppose first that $\sigma$ occurs in $\pi$ and fix an occurrence.
  Construct a matching $\mathcal{M}$ as follows:
  \begin{itemize}
    \item $\mathcal{M}$ contains $N_1$ pairwise crossing
    $(\nu_1, \nu'_1)$-edges.
    \item $\mathcal{M}$ contains $N_2$ pairwise crossing
    $(\nu_2, \nu'_2)$-edges.
    \item $\mathcal{M}$ contains $N_3$ pairwise crossing
    $(\nu_3, \nu'_3)$-edges.
    \item $\mathcal{M}$ contains $N_4$ pairwise crossing
    $(\nu_4, \nu'_4)$-edges.
    \item $\mathcal{M}$ contains $k+2$ pairwise crossing
    $(\sigma', \pi')$-edges as depicted in
    Fig.~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely,
    (i) the first position of $\sigma'$
    (\emph{i.e.}, $(2N_1+N_2+N_3) + 1$) is linked
    to the first position of $\pi'$
    (\emph{i.e.}, $(2N_1 + 2N_2 + 2N_3 + N_4 + k + 2) + 1$),
    (ii) the last position of $\sigma'$
    (\emph{i.e.}, $(2N_1+N_2+N_3) + k+2$) is linked
    to the last position of $\pi'$
    (\emph{i.e.}, $(2N_1 + 2N_2 + 2N_3 + N_4 + k + 2) + n+2$),
    and all other positions in $\sigma'$ are linked by means of $k$ pairwise
    crossing edges to the positions in
    $\pi'$ that correspond to the fixed occurence of $\sigma$ in $\pi$.
    (Notice that we use here the fact that $\sigma$ occurs in $\pi$).
    \item $\mathcal{M}$ contains $n-k$ pairwise crossing
    $(\pi', \pi'')$-edges as depicted in
    Fig.~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely,
    all positions in $\pi'$ that do not correspond to the fixed occurence of
    $\sigma$ in $\pi$ are linked by means of $n-k$ pairwise crossing edges
    to the positions in $\pi''$ that do not correspond to the fixed
    occurrence of $\sigma$ in $\pi$.
    \item $\mathcal{M}$ contains $k$ pairwise crossing
    $(\pi'', \sigma'')$-edges as depicted in
    Fig.~\ref{fig:subfig:sigma' - pi' - pi'' - sigma''}.
    More precisely, the positions in $\pi''$ that correspond to
    the fixed occurrence of $\sigma$ in $\pi$ are llinked
    linked by means of $k$ pairwise crossing edges to all positions in
    $\sigma''$.
    (Notice that we use here the fact that $\sigma$ occurs in $\pi$.)
  \end{itemize}
  It can be easily checked (probably referring to Fig.~\ref{fig:reduction}) that
  $\mathcal{M}$ is perfect, containment-free, and that
  for any two disctinct edges
  $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.

@@

        input permutations $\sigma = 312$ and $\pi = 4\mathbf{5}\mathbf{2}1\mathbf{3}6$

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_1, \nu_2)$-edge $e = (a, a')$ in $\mathcal{M}$.
    Under this assumption, we show that $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Indeed, suppose, aiming at a contradiction,
    that there exists a $(\nu_1, \nu_1)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free,
    we must have $x < a$.
    Then it follows that $\mu(x) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(x') > \mu(a')$ (since $\nu_1$ is above $\nu_2$),
    which contradicts our hypothesis about $\mathcal{M}$.
    Hence $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Furthermore, since $\nu_1$ is increasing and
    there exists only one $(\nu_1, \nu_2)$-edge $(a, a')$ in $\mathcal{M}$,
    we conclude that
    $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges.
    But $|\nu_1| = |\nu'_1| = N_1$ and $\mathcal{M}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-edge,
      say $(y', y)$. Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item Position $y$ is not involved in a $(\nu_2, \nu'_1)$-edge.
      Since $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges
      in $\mathcal{M}$ and $|\nu'_1| = N_1$, there exists an edge $(y, y'')$ in $\mathcal{M}$
      that is neither a $(\nu_1, \nu'_1)$-edge nor a $(\nu_2, \nu'_1)$-edge
      nor a $(\nu'_1, \nu'_1)$-edge.
      In other words, $y'' > 2N_1 + N_2$.
      Now, for any $(\nu_1, \nu'_1)$-edge $(x, x')$ in $\mathcal{M}$, we
      have $\mu(x) < \mu(y)$ (since $\nu_1$ is below $\nu'_1$)
      and $\mu(x') > \mu(y'')$ (since $\nu'_1$ is above any other gadget),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:(nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then it follows that there exists an edge $(x, x')$ in $\mathcal{M}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-edge (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$ (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ is containment-free,
    there is neither a $(\nu_2, \nu_2)$-edge nor a $(\nu'_1, \nu'_1)$-edge
    in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an edge $(y, y')$ of $\mathcal{M}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would not be containment-free).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an edge in $\mathcal{M}$.
    Then it follows that $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:(nu_1, nu'_1)-edge} with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor a $(\nu_1, \nu'_1)$-edge
    nor a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:(nu_2, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is no
    $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
    Notice that there is neither
    a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_2, \nu_2)$-edge (Claim~\ref{claim:no (nu_2, nu_2)-edge})
    nor a $(\nu_2, \nu'_1)$-edge (Claim~\ref{claim:no (nu_2, nu'_1)-edge})
    in $\mathcal{M}$.
    But $|\nu_2| = N_2 > 2N_3 + 2N_4 + 2n + 2k +4$.
    Hence $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no edge below (nu_2, nu'_2)-edge}]
    Combine Claim~\ref{claim:(nu_2, nu'_2)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim: no edge right of nu'_2}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ contains an edge $(a, a')$ which is
    either a $(\nu'_2, \nu'_3)$-edge
    or a $(\nu'_2, \pi')$-edge
    or a $(\nu'_2, \nu'_4)$-edge
    or a $(\nu'_2, \pi'')$-edge
    or a $(\nu'_2, \sigma'')$-edge.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge},
    there exists a $(\nu_2, \nu'_2)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) > \mu(a)$ (since $\nu_2$ is above $\nu'_2$) and
    $\mu(b') < \mu(a')$ (since $\nu'_3$, $\pi'$, $\nu'_4$, $\pi''$ and
    $\sigma''$ are all above $\nu'_2$),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_3, nu'_2)-edge}]
    Suppose, aiming at a contradiction, that there exists a
    $(\nu_3, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge}, there
    exists at least one $(\nu_2, \nu'_2)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free (Lemma~\ref{lemma:matching}),
    we have $x' < a'$.
    Therefore,
    we have $\mu(x) < \mu(a)$ (since $\nu_2$ is below $\nu_3$) and
    $\mu(x') > \mu(a')$ (since $\nu'_2$ is decreasing),
    which contradicts our hypothesis about $\mathcal{M}$.
    See Fig.~\ref{fig:subfig:no (nu_3, nu'_2)-edge}.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:at most one (nu_2, nu_3)-edge}]
    Apply Lemma~\ref{lemma:at most one edge monotone}.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_3)-edge and no (nu'_1, nu_3)-edge}]
    We first prove that there is no $(\nu_1, \nu_3)$-edge in $\mathcal{M}$.
    Indeed, suppose, aiming at a contradiction, that these exists
    a $(\nu_1, \nu_3)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have
    $b < a'$.
    Then it follows that
    $\mu(b) < \mu(a)$ (since $\nu_1$ is incresing) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu_3$),
    which contradicts our hypothesis about~$\mathcal{M}$.

    As for no $(\nu_1, \nu_3)$-edges in $\mathcal{M}$, suppose,
    aiming at a contradiction, that there exists
    a $(\nu'_1, \nu_3)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that
    $\mu(b) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu_3$),
    which contradicts our hypothesis about~$\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:(nu_3, nu'_3)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_3, \nu'_3)$-edge in $\mathcal{M}$.
    Combining
    Claim~\ref{claim:no edge below (nu_2, nu'_2)-edge},
    Claim~\ref{claim:no (nu_3, nu'_2)-edge},
    Claim~\ref{claim:at most one (nu_2, nu_3)-edge}
    and Claim~\ref{claim:no (nu_1, nu_3)-edge and no (nu'_1, nu_3)-edge},
    we conclude that $N_3-1$ positions in $\nu_3$ are involved
    in edges of $\mathcal{M}$ that are
    neither ($\nu_1, \nu_3)$-edges,
    nor $(\nu_2, \nu_3)$-edges
    nor $(\nu'_1, \nu_3)$-edges
    nor $(\nu_3, \nu_3)$-edges.
    But $N_3 - 1 > 2N_4 + 2n + 2k + 4$ (the positions left) and hence
    $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_3, nu'_3)-edge}]
    Combine Claim~\ref{claim:(nu_3, nu'_3)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}
  \bigskip

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_4)-edge}]
    According to Claim~\ref{claim:all (nu_2, nu'_2)-edges},
    all positions in $\nu_2$ and $\nu'_2$ are involved in
    $(\nu_2, \nu'_2)$-edges in $\mathcal{M}$.
    \qed
  \end{proof}
  \bigskip
